Web Service Community \\ Learning

### 2014-06-21 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

\author{Michael~Shell,~\IEEEmembership{Member,~IEEE,}
        John~Doe,~\IEEEmembership{Fellow,~OSA,}
        and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem M. Shell is with the Department
of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
GA, 30332.\protect\\
% note need leading \protect in front of \\ to get a newline within \thanks as
% \\ is fragile and will error, could use \hfil\break instead.
E-mail: see http://www.michaelshell.org/contact.html
\IEEEcompsocthanksitem J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
\thanks{}}

@@

\section{Preliminaries}\label{s:preliminaries}
text text

\section{Problem Formulation and Modeling}\label{s:model}

\section{Web Service}\label{s:web_service}

>>>>

\author{Michael~Shell,~\IEEEmembership{Member,~IEEE,}
        John~Doe,~\IEEEmembership{Fellow,~OSA,}
        and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem TestName is with the Department
of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
GA, 30332.\protect\\
% note need leading \protect in front of \\ to get a newline within \thanks as
% \\ is fragile and will error, could use \hfil\break instead.
E-mail: see http://www.michaelshell.org/contact.html
\IEEEcompsocthanksitem J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
\thanks{}}

@@

\section{The Model}\label{s:preliminaries}
In this section, we first present the architecture of the proposed model. We explore the characterestic of intelligent service agents and the way we train them. ...

\subsection{Web Services}\label{s:ws}

Over the past years, online services have become part of standard daily life of people around the globe. Many modern applications rely on web services from different providers. For instance, many mobile and tablet applications which have limited storage and processing power are merely interfaces aggregating different information from online services. Examples are vast, weather forecasting, ticket selling, shopping apps, local maps and places searching.

The World Wide Web Consortium (W3C) defines web services as follows: ``software system designed to support interpretable machine-to-machine interaction over a network. It has an interface described in a machine-processable format (specifically WSDL). Other systems interact with the web service in a manner prescribed by its description using SOAP messages, typically conveyed using HTTP with XML serialization in conjunction with other Web-related standards''. When developers declare a new web service, it will be
discovered based on its description that fully discloses its functionalities. Developers also have to declare a public interface and a readable documentation to help other developers when integrating different services \cite{w3cwsdl}. Nowadays, web API standards which do not require XML-based web service protocols like SOAP and WSDL are also emerging. They are also called REST (representational state transfer) services which are moving towards simpler communication protocols. 
%They are not restricted 
%to XML formats, recently JSON, a human readable and simpler format 
%is becoming popular among online service providers.

We are not going to delve into engineering details of online web service implementation and its protocols in this proposal. We are interested in web services from their business model perspective. Service providers usually charge end users for services they provide. For example, Google has listed their pricing and plans for wide range of services they provide on their web service console page\footnote{https://code.google.com/apis/console}.

In our research work, we abstract web services as rational agents\footnote{The term rational is used here in the sense that web services are utility maximizers} providing services to end users. They aim to maximize their individual income by receiving enough requests from end users. In order to increase their revenue, web services seek for more tasks if they have the capacity and throughput to do so. Web services can join communities to have better efficiency by collaborating with others, to have access to broad market share, and to have opportunity of receiving a bigger task pool from end users. Furthermore, the high reliance on web services has increased quality expectations from end users. Communities of web services can provide higher availability, performance, reliability, and recovery for end users.

\subsection{Web Service Communities}\label{s:wsc}

Figure \ref{fig_community} represents the architecture of web service communities. The community is essentially a virtual group of web services having similar and complementary functionalities. Communities aggregate web services and communicate with other entities such as UDDI registries and users, using identical protocols as single web services. Web services join communities to increase their utility by having a larger market share and task pool. Community coordinators are responsible for community development, managing membership requests from web services and distributing user tasks among the community members. Community coordinators try to attract quality web services for joining and keep the community as stable and productive as possible to gain better reputation and user satisfaction, which results in having a higher market share for the community. The way the web services reside inside communities and how communities of web services are engineered is described comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}.

\begin{figure*}%[!t]
\centerline{\includegraphics[width=6.25in]{figures/community.eps}}
\caption{Architecture of web service communities}
\label{fig_community}
\end{figure*}

\subsection{Internal Features}\label{s:if}

\subsection{External Features}\label{s:ef}

\subsection{The join challange}\label{s:tjc}

\subsection{Join Consiquences}\label{s:jc}
